### 2021-05-27 shared/analysis.tex
WIP : QSORT

For each of the random run we maintain a variable $count_j$ that tells us the total number of comparision that happened in a particular random run $j$.

We want to $assert$ the following.

\begin{equation}
	E[count_j] = n * log(n) \enspace \mid \enspace \forall j \in random \enspace runs.
\end{equation}

>>>>

The probability mass associated with the $i_{th}$ random run as is given below considering each $pivot$ selection being an independent selection.

\begin{equation}
	w_i = (1 / n) * \prod_{j=1}^{k} 1 / l_j  * \prod_{j=1}^{k} 1 / r_j \quad \mid \quad for \enspace k-partitons
\end{equation}

\begin{equation}
	where \enspace l_j = count(l_{terms}), \enspace r_j = count(r_{terms}) \quad \mid \quad in \enspace j^{th} \enspace partition. 
\end{equation}
